Universal Anonymous Signatures

### 2022-05-13 prism-backend/research/gsac/model-gsac.tex
Added sketch of security proof for SBCM. Updated GSAC model to include attrs on Open. Other minor edits.
Updated GSAC and UAS proofs based on updated non-frame definiton.
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.
Quick full pass (excl. appendices).

We also need to take into account that, in group signature schemes, users only
get one membership credential -- typically bound to their personal secret
key --, which they then use to create as many group signatures as they want. On
the other hand, in anonymous credentials, users can get as many credentials as
they desire, which can (typically) then be showed also arbitrarily many times.
In this regard, we follow a somehow intermediate approach: users own a single
personal secret key, which they can use to get as many credentials as they wish.
Subsequently, they can use any of those credentials to create \GSAC signatures.
This has, as expected, some nuanced impact in the modelling. For instance, in
group signatures, tracing and non-frameability are frequently dependent on the
open function, which (among other things) returns an index pointing to the join
transcript associated with the user who produced the signature given by the
adversary as a response to the game's challenge. In our approach, though, each
user may have many such transcripts -- one per credential that the user
obtains. However, note that what actually provides meaning to these notions
is not the index; but the associated user key pair, which is moreover necessary
to prove that the opening has been performed honestly. Thus, with some
restructuring of the corresponding games, we can still capture the main
meaning of these traceability and non-frameability notions from group
signatures. This also impacts anonymity, since in group signatures, this is
modelled by challenging the adversary to guess which user (which implicitly
translates to ``which user credential'') out of two challenge users was
leveraged to produce the challenge signature. But again, in our case, users may
have multiple credentials. However, it seems sufficient to adopt a similar
anonymity flavour to that of anonymous credentials, where the adversary has to
distinguish between presentations (signatures) produced from two arbitrary
credentials, independently on whether these credentials were obtained by the
same user, or not.
%
Getting closer to the anonymity definition of anonymous credentials also has the
side effect to introduce the notions of attributes for free into the domain of
group signatures -- which, up to now, had considered membership credentials
\emph{without} attributes. Yet another side effect of introducing multiple
attributes (if we think from a group signature perspective) is that, in order
to avoid trivial wins, the anonymity game has to enforce that both challenge
credentials reveal the same predicate on their attributes.

In the model described below, we follow closely the definitions from
\cite{bsz05} for group signatures, and \cite{fhs19} for anonymous credentials
(which are in turn influenced by \cite{bsz05}).

@@

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm)$.] Given global system parameters
  \parm, returns the issuer's key pair. Hereafter, we assume that the public
  part \ipk is added to the group public key \gpk.
\item[$(\opk,\osk) \gets \OKeyGen(\parm)$.] Given global system parameters
  \parm, returns an opener's key pair. Hereafter, we assume that the public part
  \opk is added to the group public key \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's key pair.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle \Obtain(\gpk,\usk,\attrs),\Issue(\gpk,\isk,\attrs) \rangle$.]
  This interactive protocol lets a user with key pair (\upk,\usk) running the
  \Obtain process, obtain a credential \cred with attributes \attrs, by
  communicating with an issuer, with private key \isk, running the \Issue
  counterpart. The user outputs the produced credential \cred, while the issuer
  outputs the protocol transcript \utrans for the produced credential.
\item[$\sig \gets \Sign(\gpk,\usk,\cred,\dattrs,\msg)$.] The user with
  with secret key \usk, who obtained a credential \cred, produces a signature
  \sig over message \msg, revealing subset of attributes \dattrs in \cred.
\item[$1/0 \gets \Verify(\gpk,\sig,\dattrs,\msg)$.] Checks whether \sig is a
  valid signature revealing the attribute set \dattrs of its signing credential,
  over message \msg.
\item[$(\upk,\oproof)/\bot \gets
  \Open(\gpk,\osk,\sig,\dattrs,\msg)$.]
  Given a signature \sig over message \msg, produced by a credential with
  attributes containing the set \dattrs, returns the public key \upk of the
  signer, and a proof of opening correctness \oproof; or $\bot$ if the
  opening process fails.
\item[$1/0 \gets \Judge(\gpk,\upk,\oproof,\sig,\dattrs,
  \msg)$.] Checks if \oproof is a valid opening correctness proof stating that
  the user with key \upk generated signature \sig over message \msg, revealing
  attributes $\dattrs$. 
\end{description}

The correctness and security properties are defined with the help of the
following sets of oracles, and global variables that help oracles and games
keep consistent state.

\paragraph{Global variables.} %
All the honestly generated users (i.e., all honestly generated user key pairs,
since we assume a one-to-one relationship between user and user key pair), as
well as all honestly generated credentials, are assigned identifiers. We
typically write \uid for users' identifiers, and \cid for credentials'. The
adversary can
refer to any individual user or credential using the corresponding identifier --
even though he may not know the actual contents of the key pairs or credentials.
In games that involve challenge user or credential identifiers, we use \cuid and
\ccid to refer to these challenge user/credential.
%
The games keep track of the user keys (through set \UK) and credentials (through
table \CRED) that are created as a result of oracle calls by the adversary. We
use the user and credential identifiers to reference specific user key pairs,
credentials, and credential attributes.
For instance, $\UK[\uid]$ refers to the user key pair corresponding to user
with identifier \uid, $\PUBUK[\uid]$ refers to the public key of that key pair,
and $\PRVUK[\uid]$ to the private key; credential $\CRED[\cid]$ refers to the
credential data associated to the credential with identifier \cid; $\ATTR[\cid]$
is the set of attributes that was assigned to the credential with identifier
\cid; and $\OWNR[\cid]$ is set to the \uid corresponding to the user that
credential \cid was issued to.
%
Additionally, the games keep track of all honest and corrupt users that have
been generated, through sets \HU and \CU, respectively. They also keep track of
the signatures that have been honestly produced, through the \SIG table. Since
signatures are produced through credentials, the \SIG table is indexed with
{\cid}s. For the anonymity game, we also need to keep track of the challenge
signatures that the adversary has obtained, in order to prevent trivial wins
by allowing any of them to be opened. 
%
All global variables are assumed to be initially set by the games to empty
values, and all tables/sets are initialized as empty tables/sets. Also, for
readability, we abuse the syntax as follows: we
write $\CRED[\uid]$ to mean $\CRED[\cid]$ for all $\cid$ such that
$\OWNR[\cid] = \uid$.% ; we also sometimes use \upk as a ``synonym'' of \uid, as it
% is possible to do a reverse lookup from the \UK table (i.e., $\CRED[\upk]$ can
% be replaced by $\CRED[\uid]~\st~\UK[\uid]=(\upk,\cdot)$); \todo{Something else?}

@@

\begin{description}
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
  the user's key pair.
\item[\CUGEN.] If the specified user identifier is not already in the game,
  sets the user public key to a value given by the adversary. If it already
  exists, and is associated to an honest user, then it reveals to the adversary
  the user's secret key.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
  in games that support it, by letting it interact with honest users who want to
  receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, lets the adversary learn
  the public key of the user who produced it.
\item[\CHALb.] Upon receiving two challenge credentials, a common intersecting
  set of attributes, and a message, returns a signature produced by one of these
  two credentials, defined by the bit $b$, which is established in the anonymity
  game.
\end{description}

\paragraph{Correctness.} %
Correctness of \GSAC schemes is formalized through the experiment in
\figref{fig:exp-gsac-corr}. It states that a signature for some message \msg,
revealing attributes \dattrs, which was honestly produced through a credential
that was obtained by an honest user interacting with an honest issuer, with a
set of attributes \attrs such that $\dattrs \subseteq \attrs$, must be accepted
by \Verify. Moreover, an honestly produced correctness proof of opening for such
signature, revealing the public key pair of the user, must also be accepted by
\Judge.

@@

\begin{figure}[htp!]
  \procedure{$\ExpGSACCorrect(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
     \gpk \gets (\ipk,\opk) \\
    (\cid,\dattrs,\msg) \gets \adv^{\HUGEN,\OBTISS,\RREG}(\gpk) \\
    \pcif \dattrs \nsubseteq \ATTR[\cid] :
    \pcreturn \bot \\
    \sig \gets \Sign(\gpk,\PRVUK[\OWNR[\cid]],\CRED[\cid],\dattrs,\msg) \\
    (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\dattrs,\msg) \\
    \pcif \Verify(\gpk, \sig, \dattrs,\msg) = 0 \lor
    \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 0: \\
     \pcind \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Correctness experiment for \GSAC schemes.}
  \label{fig:exp-gsac-corr}
\end{figure}

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACTrace(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
    \gpk \gets (\ipk,\opk) \\
    (\sig,\dattrs,\msg) \gets
    \adv^{\HUGEN,\CUGEN,\RREG,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
    \pcif \Verify(\gpk,\sig,\dattrs,\msg) = 0: \pcreturn 0 \\
    \pcif \Open(\gpk,\osk,\trans,\sig,\dattrs,\msg) = \bot: \pcreturn 1 \\
    \textrm{Let}~(\upk,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,\dattrs,\msg) \\
    \pcif \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 0: \pcreturn 1 \\
    \pcelse \pcif \forall \uid \in \CU \cup \HU, \nexists (\uid,\cdot,\attrs)
    \in \CRED~\st~\dattrs \subseteq \attrs: \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Traceability experiment for \GSAC schemes.}
  \label{fig:exp-gsac-trace}
\end{figure}

@@

\paragraph{Non-frameability.} %
Non-frameability variants are a core unforgeability-type property in group
signatures. However, no similar property is modelled for anonymous credentials
(see the discussion in \todo{\secref{sec:introduction}} for further detail). It
is a quite strong
property, as it must be ensured even in the presence of dishonest issuer and
opener. Intuitively, it prevents the adversary from creating a signature that
frames an honest user. Depending on the inspection capabilities of the scheme,
this framing could be done in different ways; i.e., by convincing third parties
that signatures by different (possibly corrupt) users are linked, or directly
by having open proofs output the identity of a user who did not create the
signature being opened.
%
In \GSAC schemes, in order for a user to be framed, the adversary first needs to
create a $(\sig,\dattrs,\msg,\upk,\oproof)$ tuple such that the signature,
attributes, and message are accepted by \Verify, and which, along with the user
public key, and open correctness proof, are accepted by \Judge.
Then, the adversary wins the game if the owner of the credential is honest, but
the signature was not produced via the \SIGN oracle.

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACNonframe(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
     \gpk \gets (\ipk,\opk) \\
     (\sig,\dattrs,\msg,\upk,\oproof) \gets
     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN}(\gpk,\isk,\osk) \\
     \textrm{Let}~\uid~\textrm{be st}~\PUBUK[\uid] = (\upk,\cdot) \\
     \pcreturn 1~\pcif \Verify(\gpk,\sig,\dattrs,\msg) = 1 \land 
     \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 1~\land \\
     \pcind \uid \in \HU \land \sig \notin \SIG[\uid] \\
     \pcreturn 0
  }
  \caption{Non-frameability experiment for \GSAC schemes.}
  \label{fig:exp-gsac-frame}
\end{figure}

>>>>

We also need to take into account that, in group signature schemes, users only
get one membership credential -- typically bound to their personal secret
key --, which they then use to create as many group signatures as they want. On
the other hand, in anonymous credentials, users can get as many credentials as
they desire, which can (typically) then be showed also arbitrarily many times.
In this regard, we follow a somehow intermediate approach: users own a single
personal secret key, which they can use to get as many credentials as they wish.
Subsequently, they can use any of those credentials to create \GSAC signatures.
This has, as expected, some nuanced impact in the modelling. For instance, in
group signatures, tracing and non-frameability are frequently dependent on the
open function, which (among other things) returns an member index. In our
approach, though, each user may have many such transcripts -- one per credential
that the user obtains. However, note that what actually provides meaning to
these notions is not the index; but the attributes in the credential, which is
moreover necessary
to prove that the opening has been performed honestly. Thus, with some
restructuring of the corresponding games, we can still capture the main
meaning of these traceability and non-frameability notions from group
signatures. This also impacts anonymity, since in group signatures, this is
modelled by challenging the adversary to guess which user (which implicitly
translates to ``which user credential'') out of two challenge users was
leveraged to produce the challenge signature. But again, in our case, users may
have multiple credentials. However, it seems sufficient to adopt a similar
anonymity flavour to that of anonymous credentials, where the adversary has to
distinguish between presentations (signatures) produced from two arbitrary
credentials, independently on whether these credentials were obtained by the
same user, or not.
%
Getting closer to the anonymity definition of anonymous credentials also has the
side effect to introduce the notions of attributes for free into the domain of
group signatures -- which, up to now, had considered membership credentials
\emph{without} attributes. Yet another side effect of introducing multiple
attributes (if we think from a group signature perspective) is that, in order
to avoid trivial wins, the anonymity game has to enforce that both challenge
credentials reveal the same predicate on their attributes.

@@

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm)$.] Given global system parameters
  \parm, returns the issuer's key pair. Hereafter, we assume that the public
  part \ipk is added to the group public key \gpk.
\item[$(\opk,\osk) \gets \OKeyGen(\parm)$.] Given global system parameters
  \parm, returns an opener's key pair. Hereafter, we assume that the public part
  \opk is added to the group public key \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's key pair.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle \Obtain(\gpk,\usk,\attrs),\Issue(\gpk,\isk,\attrs) \rangle$.]
  This interactive protocol lets a user with key pair (\upk,\usk) running the
  \Obtain process, obtain a credential \cred with attributes \attrs, by
  communicating with an issuer, with private key \isk, running the \Issue
  counterpart. The user outputs the produced credential \cred, while the issuer
  outputs the protocol transcript \utrans for the produced credential.
\item[$\sig \gets \Sign(\gpk,\usk,\cred,\dattrs,\msg)$.] The user with
  with secret key \usk, who obtained a credential \cred, produces a signature
  \sig over message \msg, revealing subset of attributes \dattrs in \cred.
\item[$1/0 \gets \Verify(\gpk,\sig,\dattrs,\msg)$.] Checks whether \sig is a
  valid signature revealing the attribute set \dattrs of its signing credential,
  over message \msg.
\item[$(\upk,\attrs,\oproof)/\bot \gets
  \Open(\gpk,\osk,\sig,\dattrs,\msg)$.]
  Given a signature \sig over message \msg, produced by a credential with
  attributes containing the set \dattrs, returns the public key \upk of the
  signer, and the attribute set \attrs contained in the credential used to
  generate the signature, along with a proof of opening correctness \oproof; or
  $\bot$ if the opening process fails.
\item[$1/0 \gets \Judge(\gpk,\upk,\attrs,\oproof,\sig,\dattrs,
  \msg)$.] Checks if \oproof is a valid opening proof for the
  statement: ``The owner of a credential over attribute set \attrs, and owner
  of public key \upk, created signature \sig, which reveals attribute set
  $\dattrs \subseteq \attrs$''.
\end{description}

The correctness and security properties are defined with the help of the
following sets of oracles and global variables that help oracles and games
keep consistent state.

\paragraph{Global variables.} %
All the honestly generated users (i.e., all honestly generated user key pairs,
since we assume a one-to-one relationship between user and user key pair), as
well as all honestly generated credentials, are assigned identifiers. We
typically write \uid for users' identifiers, and \cid for credentials'. The
adversary can
refer to any individual user or credential using the corresponding identifier --
even though he may not know the actual contents of the key pairs or credentials.
In games that involve challenge user or credential identifiers, we use \cuid and
\ccid to refer to these challenge user/credential.
%
The games keep track of the user keys (through table \UK) and credentials (through
table \CRED) that are created as a result of oracle calls by the adversary. We
use the user and credential identifiers to reference specific user key pairs,
credentials, and credential attributes.
For instance, $\UK[\uid]$ refers to the user key pair corresponding to user
with identifier \uid, $\PUBUK[\uid]$ refers to the public key of that key pair,
and $\PRVUK[\uid]$ to the private key; credential $\CRED[\cid]$ refers to the
credential data associated to the credential with identifier \cid; $\ATTR[\cid]$
is the set of attributes that was assigned to the credential with identifier
\cid; and $\OWNR[\cid]$ is set to the \uid corresponding to the user that
credential \cid was issued to.
%
Additionally, the games keep track of all honest and corrupt users that have
been generated through sets \HU and \CU, respectively. They also keep track of
the signatures that have been honestly produced, through the \SIG table. Since
signatures are produced through credentials, the \SIG table is indexed with
{\cid}s. For the anonymity game, we also need to keep track of the challenge
signatures that the adversary has obtained, in order to prevent trivial wins
by allowing any of them to be opened. 
%
All global variables are assumed to be initially set by the games to empty
values, and all tables/sets are initialized as empty tables/sets. Also, for
readability, we abuse the syntax and
write $\CRED[\uid]$ to mean $\CRED[\cid]$ for all $\cid$ such that
$\OWNR[\cid] = \uid$.% ; we also sometimes use \upk as a ``synonym'' of \uid, as it
% is possible to do a reverse lookup from the \UK table (i.e., $\CRED[\upk]$ can
% be replaced by $\CRED[\uid]~\st~\UK[\uid]=(\upk,\cdot)$); \todo{Something else?}

@@

\begin{description}
\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
  the user's key pair.
\item[\CUGEN.] If the specified user identifier is not already in the game,
  sets the user public key to a value given by the adversary. If it already
  exists, and is associated to an honest user, then it reveals to the adversary
  the user's secret key.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
  in games that support it, by letting it interact with honest users who want to
  receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.  
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, lets the adversary learn
  the public key of the user who produced it.
\item[\CHALb.] Upon receiving two challenge credentials, a common intersecting
  set of attributes, and a message, returns a signature produced by one of these
  two credentials, defined by the bit $b$, which is established in the anonymity
  game.
\end{description}

\paragraph{Correctness.} %
Correctness of \GSAC schemes is formalized through the experiment in
\figref{fig:exp-gsac-corr}. It states that a signature for some message \msg,
revealing attributes \dattrs, which was honestly produced through a credential
that was obtained by an honest user interacting with an honest issuer, with a
set of attributes \attrs such that $\dattrs \subseteq \attrs$, must be accepted
by \Verify. Moreover, an honestly produced correctness proof of opening for such
signature, revealing the public key pair of the user and credential attributes,
must also be accepted by \Judge.

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACCorrect(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
     \gpk \gets (\ipk,\opk) \\
    (\cid,\dattrs,\msg) \gets \adv^{\HUGEN,\OBTISS,\RREG}(\gpk) \\
    \pcif \dattrs \nsubseteq \ATTR[\cid] :
    \pcreturn \bot \\
    \sig \gets \Sign(\gpk,\PRVUK[\OWNR[\cid]],\CRED[\cid],\dattrs,\msg) \\
    (\upk,\attrs,\oproof) \gets \Open(\gpk,\osk,\sig,\dattrs,\msg) \\
    \pcif \Verify(\gpk, \sig, \dattrs,\msg) = 0 \lor
    \Judge(\gpk,\upk,\attrs,\oproof,\sig,\dattrs,\msg) = 0: \\
     \pcind \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Correctness experiment for \GSAC schemes.}
  \label{fig:exp-gsac-corr}
\end{figure}

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACTrace(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
    \gpk \gets (\ipk,\opk) \\
    (\sig,\dattrs,\msg) \gets
    \adv^{\HUGEN,\CUGEN,\RREG,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
    \pcif \Verify(\gpk,\sig,\dattrs,\msg) = 0: \pcreturn 0 \\
    \pcif \Open(\gpk,\osk,\trans,\sig,\dattrs,\msg) = \bot: \pcreturn 1 \\
    \textrm{Let}~(\upk,\attrs,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,
    \dattrs,\msg) \\
    \pcif \Judge(\gpk,\upk,\attrs,\oproof,\sig,\dattrs,\msg) = 0: \pcreturn 1 \\
    \pcelse \pcif \forall \uid \in \CU \cup \HU, \nexists (\uid,\cdot,\attrs)
    \in \CRED \lor \dattrs \not\subseteq \attrs: \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Traceability experiment for \GSAC schemes.}
  \label{fig:exp-gsac-trace}
\end{figure}

@@

\paragraph{Non-frameability.} %
Non-frameability variants are a core unforgeability-type property in group
signatures. However, no similar property is modelled for anonymous credentials.
It is a quite strong
property, as it must be ensured even in the presence of dishonest issuer and
opener. Intuitively, it prevents the adversary from creating a signature that
frames an honest user. Depending on the inspection capabilities of the scheme,
this framing could be done in different ways; i.e., by convincing third parties
that signatures by different (possibly corrupt) users are linked, or directly
by having open proofs output the identity of a user who did not create the
signature being opened.
%
In \GSAC schemes, in order for a user to be framed, the adversary first needs to
create a $(\sig,\dattrs,\msg,\upk,\attrs,\oproof)$ tuple such that the signature,
attributes, and message are accepted by \Verify, and which, along with the user
public key, and open correctness proof, are accepted by \Judge; or, alternatively,
produce a signature revealing \dattrs, which is accepted by \Verify, and \Judge
accepts \attrs as the attribute set in the used credential owned by \upk, but
$\dattrs \not\subseteq \attrs$.
Then, the adversary wins the game if the owner of the credential is honest, but
the signature was not produced via the \SIGN oracle.

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACNonframe(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
     \gpk \gets (\ipk,\opk) \\
     (\sig,\dattrs,\msg,\upk,\attrs,\oproof) \gets
     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN}(\gpk,\isk,\osk) \\
     \pcif \Verify(\gpk,\sig,\dattrs,\msg) = 0: \pcreturn 0 \\
     \pcif \Judge(\gpk,\upk,\attrs,\oproof,\sig,\dattrs,\msg) = 0: \pcreturn 0 \\
     \textrm{Let}~\uid~\textrm{be st}~\PUBUK[\uid] = (\upk,\cdot) \\
     \pcif \textrm{no such \uid exists}: \pcreturn 0 \\
     \pcif \uid \in \HU \land (\sig \notin \SIG[\uid]
     \lor \dattrs \not\subseteq \attrs): \pcreturn 1 \\
     \pcreturn 0
  }
  \caption{Non-frameability experiment for \GSAC schemes.}
  \label{fig:exp-gsac-frame}
\end{figure}
